An asymptotically normal out-of-sample test based on mixed estimation windows

### 2017-05-18 S2-normality.tex
Automatic equation renumbering
This commit renumbers the equations in the paper so that they
are in order and are (more importantly) unique.

Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$, that $v_t$ is another random process that is believed to
potentially contain information about $y_{t+1}$, and that
$(y_t, x_t, v_t)$ is stationary and weakly dependent.
In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient for the regression of $y_{t+1}$ on $x_t$ and define
$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
to $\sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$
and we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
with $R$ an arbitrary starting value
and $P = T - R$.

Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
\end{equation}
almost surely.
\citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
$R$ to estimate $\yh_{t+1}$,%
\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
and $R$ is kept finite as $T \to \infty$ so that
$\yh_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window prevents
the degeneracy that can arise when comparing nested models out-of-sample (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the \oos\ average remains positive and the average obeys a \clt.%
\footnote{This approach was first introduced by \citet{GiW:06}.} %

@@

This paper proposes using the same basic \oos\ statistic,
but using a recursive window to estimate $\btrue$ and produce
$\eph_{t+1}$:
\begin{align}
  \label{eq:8}
  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
  \sum_{s=1}^{t-1} x_{s} y_{s+1}
  && \text{and}
  &
  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
\end{align}
for each $t$.%
\footnote{The matrix inversion in $\bh_t$ can be replaced with a
  pseudo-inverse if necessary for some values of $t$ without changing
  the forecast.} %
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under Clark and West's
\mds\ null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
another forecast of $y_{t+1}$ based on a fixed-length rolling window.

@@

Consider the following environment. There is a single linear
benchmark model of the target variable, $y_{t+1}$:
\begin{equation}\label{eq:1}
  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T-1
\end{equation}
where $\beta$ is an unknown vector of parameters and $x_t$ is an
observed vector of predictors. The parameter $\beta$ is estimated with
\ols\ using a recursive window as described by Equation~\eqref{eq:8}.
The alternative model is denoted $\yh_{t+1}$ and is estimated with a
rolling window of length $R$.

@@

\phantomsection
\addcontentsline{toc}{subsubsection}{Assumption \ref{a3}}
\begin{asmp}\label{a3}%
  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
  with a recursive window according to~\eqref{eq:8}. The alternative
  forecast satisfies
  \begin{equation}
    \yh_{t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
  \end{equation}
  where $\psi$ is a known measurable function and the window length,
  $R$, remains finite as $T \to \infty$. Moreover, the vector
  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments
  where $r$ is first defined in Assumption~\ref{a1}.
\end{asmp}

>>>>

Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$, that $v_t$ is another random process that is believed to
potentially contain information about $y_{t+1}$, and that
$(y_t, x_t, v_t)$ is stationary and weakly dependent.
In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient for the regression of $y_{t+1}$ on $x_t$ and define
$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
to $\sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$
and we can see immediately that
\begin{equation}
  \label{eq:1}
  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
with $R$ an arbitrary starting value
and $P = T - R$.

Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:2}
  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
\end{equation}
almost surely.
\citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
Equation~\eqref{eq:2}, but use a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
$R$ to estimate $\yh_{t+1}$,%
\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
and $R$ is kept finite as $T \to \infty$ so that
$\yh_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window prevents
the degeneracy that can arise when comparing nested models out-of-sample (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the \oos\ average remains positive and the average obeys a \clt.%
\footnote{This approach was first introduced by \citet{GiW:06}.} %

@@

This paper proposes using the same basic \oos\ statistic,
but using a recursive window to estimate $\btrue$ and produce
$\eph_{t+1}$:
\begin{align}
  \label{eq:3}
  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
  \sum_{s=1}^{t-1} x_{s} y_{s+1}
  && \text{and}
  &
  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
\end{align}
for each $t$.%
\footnote{The matrix inversion in $\bh_t$ can be replaced with a
  pseudo-inverse if necessary for some values of $t$ without changing
  the forecast.} %
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under Clark and West's
\mds\ null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
another forecast of $y_{t+1}$ based on a fixed-length rolling window.

@@

Consider the following environment. There is a single linear
benchmark model of the target variable, $y_{t+1}$:
\begin{equation}\label{eq:4}
  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T-1
\end{equation}
where $\beta$ is an unknown vector of parameters and $x_t$ is an
observed vector of predictors. The parameter $\beta$ is estimated with
\ols\ using a recursive window as described by Equation~\eqref{eq:3}.
The alternative model is denoted $\yh_{t+1}$ and is estimated with a
rolling window of length $R$.

@@

\phantomsection
\addcontentsline{toc}{subsubsection}{Assumption \ref{a3}}
\begin{asmp}\label{a3}%
  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
  with a recursive window according to~\eqref{eq:3}. The alternative
  forecast satisfies
  \begin{equation}
    \yh_{t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
  \end{equation}
  where $\psi$ is a known measurable function and the window length,
  $R$, remains finite as $T \to \infty$. Moreover, the vector
  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments
  where $r$ is first defined in Assumption~\ref{a1}.
\end{asmp}

### 2017-05-18 X1-mathematics.tex
Automatic equation renumbering
This commit renumbers the equations in the paper so that they
are in order and are (more importantly) unique.

\subsection{Proof of Theorem \ref{res:1}}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation}\label{eq:6}
    \sqrt{P} (\fb - \E \fb^*)
    = \ocltb{t} (\fh_t - \E f_t)
      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
  \end{equation}
  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
  we can rewrite~\eqref{eq:6} as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb^*)
    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
  Lemma~\ref{res:a4} shows that
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12} \\
    \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
  w_t = o_{p}(1)$. The proof that
  \begin{equation*}
    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
  \end{equation*}
  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.

@@

We will only prove $\sigmah_2 \to^p \sigma$. The result for
$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.

  First, we can rewrite the components of the variance estimator as
  \begin{align*}
    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
    \intertext{and}
    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
  \end{align*}
  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
  $\fb - \E \fb^* \to^p 0$,
  $\gb - \E \gb^* \to^p 0$,
  \begin{gather}
    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
    \intertext{and}
    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
  \end{gather}
  The first two results are implied by the proof of
  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
  follow from the \lln, since each summand is an $L_1$-mixingale of
  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
  prove~\eqref{eq:4} and~\eqref{eq:5}.

  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
  that~\eqref{eq:4} holds if
  \begin{gather}
    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
    \intertext{and}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
  \end{gather}
  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
  \begin{align*}
    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  by Lemma~\ref{res:a2} and the \lln.
  A similar argument holds for the second term:
  \begin{align*}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
  zero in probability by construction. The proof of~\eqref{eq:5} is similar.

@@

\phantomsection
\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a4}}
\begin{alem}\label{res:a4}
  Under the conditions of Theorem~\ref{res:1}, Equations
  \eqref{eq:11}--\eqref{eq:13} hold.
\end{alem}

\begin{proof}[Proof of~\eqref{eq:11}]
Choose $\delta > 0$ and $a \in (0,1/2)$ and write
\begin{multline}\label{eq:A3}
  \WesA =
  \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert > \delta\} \\
  + \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert \leq \delta\}
\end{multline}
For any $c > 0$,
\begin{multline*}
  \Pr\Bigg[ \Big\lvert \WesA \Ind\{ \lvert (t-1)^a B H_t \rvert > \delta\} \Big\rvert > c \Bigg]
  \leq \\ \Pr\Big[\omaxb{t} \lvert (t-1)^a B H_t \rvert > \delta \Big]
\end{multline*}
which converges to zero by Lemma~\ref{res:a2}, so the first summation on
the RHS of~\eqref{eq:A3} converges to zero i.p. For the second summation,
\begin{equation*}
  \E \Bigg[ \ocltb{t} (F_t - F) B H_t
    \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}}
    \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
\end{equation*}
The expectation on the RHS is of order
$P^{-1} \sum_{t=R'}^{T-1} (t-1)^{-2a}$, since $F_t / (t-1)^a$ is an
$L_2$-mixingale of size $-1/2$ by construction (see the proof of
Lemma~\ref{res:a2} for a more detailed discussion of the mixingale
argument), and converges to zero by Kronecker's Lemma.
\end{proof}

\begin{proof}[Proof of~\eqref{eq:12}]
Note that
\begin{equation*}
  \Big\lvert \WesB \Big\rvert =
  O_p\Big(\max_{t=R',\dots,T-1} \lvert B_t - B\rvert\Big)\
  O_p\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lvert H_t \rvert \Bigg).
\end{equation*}
Lemma~\ref{res:a2} implies that the first component converges to
zero in probability, so it suffices to show that the second is
$O_p(1)$. As discussed in the proof of Lemma~\ref{res:a2},
$x_t \varepsilon_{t+1}$ is an $L_2$-mixingale
of size $-1/2$ and
\begin{equation*}
  \tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert H_t \rVert_2
  = O_p\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} t^{-1/2}\Bigg)
\end{equation*}
The last summation is $O(1)$ by Lemma A1 of \citet{Wes:96}, completing
the proof.
\end{proof}

\begin{proof}[Proof of~\eqref{eq:13}]
This proof is essentially the same as that of~\eqref{eq:12}. We have
\begin{equation*}
  \Big\lvert \WesC \Big\rvert =
  O_p\Big(\max_{t=R',\dots,T-1} \lvert B_t - B\rvert\Big)\
  O_p\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lvert (F_t - F) H_t \rvert \Bigg)
\end{equation*}
where the first component converges to zero in probability. Then
\begin{equation*}
  \tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert (F_t - F) H_t \rVert_2
  \leq \tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert F_t - F \rVert_2 \lVert  H_t \rVert_2
  = O\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert  H_t \rVert_2 \Bigg)
\end{equation*}
which is $O(1)$ as in the proof of~\eqref{eq:12}.
\end{proof}

>>>>

\subsection{Proof of Theorem \ref{res:1}}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation}\label{eq:5}
    \sqrt{P} (\fb - \E \fb^*)
    = \ocltb{t} (\fh_t - \E f_t)
      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
  \end{equation}
  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
  we can rewrite~\eqref{eq:5} as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb^*)
    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
  Lemma~\ref{res:a4} shows that
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:6} \\
    \WesB \to^{p} 0 \label{eq:7} \\
    \intertext{and}
    \WesC \to^{p} 0 \label{eq:8}
  \end{gather}
  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
  w_t = o_{p}(1)$. The proof that
  \begin{equation*}
    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
  \end{equation*}
  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.

@@

We will only prove $\sigmah_2 \to^p \sigma$. The result for
$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
2.1 for the \hac\ equivalent of Equations~\eqref{eq:9}--\eqref{eq:11}.

  First, we can rewrite the components of the variance estimator as
  \begin{align*}
    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
    \intertext{and}
    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
  \end{align*}
  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
  $\fb - \E \fb^* \to^p 0$,
  $\gb - \E \gb^* \to^p 0$,
  \begin{gather}
    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:9} \\
    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:10} \\
    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:11} \\
    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:12}
    \intertext{and}
    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:13}
  \end{gather}
  The first two results are implied by the proof of
  Theorem~\ref{res:1} and~\eqref{eq:9}, \eqref{eq:10}, and~\eqref{eq:11}
  follow from the \lln, since each summand is an $L_1$-mixingale of
  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
  prove~\eqref{eq:12} and~\eqref{eq:13}.

  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
  that~\eqref{eq:12} holds if
  \begin{gather}
    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:14}
    \intertext{and}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:15}
  \end{gather}
  The \allcaps{LHS} of~\eqref{eq:14} is bounded by
  \begin{align*}
    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  by Lemma~\ref{res:a2} and the \lln.
  A similar argument holds for the second term:
  \begin{align*}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
  zero in probability by construction. The proof of~\eqref{eq:13} is similar.

@@

\phantomsection
\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a4}}
\begin{alem}\label{res:a4}
  Under the conditions of Theorem~\ref{res:1}, Equations
  \eqref{eq:6}--\eqref{eq:8} hold.
\end{alem}

\begin{proof}[Proof of~\eqref{eq:6}]
Choose $\delta > 0$ and $a \in (0,1/2)$ and write
\begin{multline}\label{eq:A3}
  \WesA =
  \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert > \delta\} \\
  + \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert \leq \delta\}
\end{multline}
For any $c > 0$,
\begin{multline*}
  \Pr\Bigg[ \Big\lvert \WesA \Ind\{ \lvert (t-1)^a B H_t \rvert > \delta\} \Big\rvert > c \Bigg]
  \leq \\ \Pr\Big[\omaxb{t} \lvert (t-1)^a B H_t \rvert > \delta \Big]
\end{multline*}
which converges to zero by Lemma~\ref{res:a2}, so the first summation on
the RHS of~\eqref{eq:A3} converges to zero i.p. For the second summation,
\begin{equation*}
  \E \Bigg[ \ocltb{t} (F_t - F) B H_t
    \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}}
    \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
\end{equation*}
The expectation on the RHS is of order
$P^{-1} \sum_{t=R'}^{T-1} (t-1)^{-2a}$, since $F_t / (t-1)^a$ is an
$L_2$-mixingale of size $-1/2$ by construction (see the proof of
Lemma~\ref{res:a2} for a more detailed discussion of the mixingale
argument), and converges to zero by Kronecker's Lemma.
\end{proof}

\begin{proof}[Proof of~\eqref{eq:7}]
Note that
\begin{equation*}
  \Big\lvert \WesB \Big\rvert =
  O_p\Big(\max_{t=R',\dots,T-1} \lvert B_t - B\rvert\Big)\
  O_p\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lvert H_t \rvert \Bigg).
\end{equation*}
Lemma~\ref{res:a2} implies that the first component converges to
zero in probability, so it suffices to show that the second is
$O_p(1)$. As discussed in the proof of Lemma~\ref{res:a2},
$x_t \varepsilon_{t+1}$ is an $L_2$-mixingale
of size $-1/2$ and
\begin{equation*}
  \tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert H_t \rVert_2
  = O_p\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} t^{-1/2}\Bigg)
\end{equation*}
The last summation is $O(1)$ by Lemma A1 of \citet{Wes:96}, completing
the proof.
\end{proof}

\begin{proof}[Proof of~\eqref{eq:8}]
This proof is essentially the same as that of~\eqref{eq:7}. We have
\begin{equation*}
  \Big\lvert \WesC \Big\rvert =
  O_p\Big(\max_{t=R',\dots,T-1} \lvert B_t - B\rvert\Big)\
  O_p\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lvert (F_t - F) H_t \rvert \Bigg)
\end{equation*}
where the first component converges to zero in probability. Then
\begin{equation*}
  \tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert (F_t - F) H_t \rVert_2
  \leq \tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert F_t - F \rVert_2 \lVert  H_t \rVert_2
  = O\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert  H_t \rVert_2 \Bigg)
\end{equation*}
which is $O(1)$ as in the proof of~\eqref{eq:7}.
\end{proof}
